Enabling high resolution hydrologic routing with machine learning assisted waterbody classification

### 2024-03-19 manuscript/manuscript.tex
populatin
towards supplement

\title{Scalable machine learning pipelines for waterbody delineation, classification, and change detection}

@@

We used some data

@@

\begin{figure}
	\centering
	\includegraphics{../figures/single_wb}
	\caption{This is a caption}
	\label{fig:single_wb}
\end{figure}

>>>>

\title{Enabling high resolution hydrologic routing with machine learning assisted waterbody classification}

@@

The current pipeline uses CubeSat imagery with a 3-5m resolution on a near-daily timestep.

@@

\begin{figure}
	\centering
	\includegraphics[width=8cm]{../figures/single_wb}
	\caption{This is a caption}
	\label{fig:single_wb}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=12cm]{../figures/diagram_pipeline}
	\caption{This is a caption}
	\label{fig:diagram_pipeline}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=10cm]{../figures/deepwatermap_vs_ndwi}
	\caption{This is a caption}
	\label{fig:deepwatermap_vs_ndwi}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=10cm]{../figures/floodplain}
	\caption{This is a caption}
	\label{fig:floodplain}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=10cm]{../figures/accuracy}
	\caption{This is a caption}
	\label{fig:accuracy}
\end{figure}
